---
title: "Cellular localisation of FUS SNS targets"
author: "Katharina Hembach"
date: "5/10/2019"
output: 
  html_document:
    toc: true
    toc_depth: 2
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Setup

```{r packages, warning = FALSE, message = FALSE}
library(rtracklayer)
library(tximport)
library(stringr)
library(ggplot2)
library(tidyr)
library(dplyr)
library(biomaRt)
library(biomartr)
library(GO.db)
library(pathview)
library(org.Mm.eg.db)
library(annotate)
library(ggraph)
library(igraph)
library(viridis)
library(data.tree)
library(edgeR)
library(goSTAG)
```

# Reading omniCLIP peaks

We read the top peaks and and filter the top peaks based on score.

```{r omniCLIP, cache = 2}
base_dir <- "/home/Shared/data/seq/sonu_CLIPseq/clip_March2018"
gtf_file <- "/home/Shared/data/annotation/Mouse/Ensembl_GRCm38.90/gtf/Mus_musculus.GRCm38.90.gtf"

out_dir <- "/home/Shared/data/seq/sonu_CLIPseq/clip_March2018/analysis/deduplicated/clipper_omniCLIP_qc"

out_dir1 <- "/home/Shared/data/seq/sonu_CLIPseq/clip_March2018/analysis/omniCLIP/ribo0"
out_dir_top <- "/home/Shared/data/seq/sonu_CLIPseq/clip_March2018/analysis/omniCLIP/ribo0/top_100"

metadat <- read.table(file.path(base_dir, "metadata.txt"), header=TRUE)

gtf <- import(gtf_file)

cutoff <- 100

sample <- "SNS_70K"

###### Read the CLIP peaks -----------------------------------------------------
omni <- list()
omni[[sample]] <- import(file.path(base_dir,"omniCLIP", 
                                   paste0(sample, "_ribo0"),
                                   paste0(sample,"_bg_SNS_ribo0_pred.bed")))
## add a column with the gene id
omni[[sample]]$gene_id <- str_split(omni[[sample]]$name, "_", 
                                    simplify = TRUE)[,1]

### filter top peaks
omni_filtered <- list()
omni_filtered[[sample]] <- omni[[sample]][omni[[sample]]$score >= cutoff]
```


# Salmon gene expression estimates

```{r salmon, cache = 2}
## new bias corrected Salmon quantifications
salmon_base_dir <- "/home/Shared/data/seq/sonu_RNAseq/riboZero_Nov2017/rnaseqworkflow"
salmon_dir_name <- "salmon"

samples <- list.files(file.path(salmon_base_dir, salmon_dir_name), 
                      pattern = "WT_SNS_[45]")
files <- file.path(file.path(salmon_base_dir, salmon_dir_name), 
                   samples, "quant.sf")
names(files) <-  samples

grp <- str_split(samples, pattern = "_", simplify = TRUE)
grp <- as.factor(paste0(grp[ ,1], "_", grp[ ,2]))
sample_nr <- str_split(samples, pattern = "_", simplify = TRUE)[,3]

tx2gene<- unique(mcols(gtf)[c("transcript_id", "gene_id")])
tx2gene <- tx2gene[!is.na(tx2gene$transcript_id), ]
tx2gene <- tx2gene[order(tx2gene$transcript_id), ]
## gene level counts
txi <- tximport(files, type="salmon", txIn = TRUE, tx2gene = tx2gene, 
                txOut=FALSE, countsFromAbundance = "no", ignoreTxVersion = TRUE)  
# tpms <- txi$abundance  # tpm per gene

counts <- round(txi$counts)
cts <- counts[rowSums(is.na(counts)) == 0, ]

## add average transcript lengths as offset
normMat <- txi$length[match(rownames(cts), rownames(txi$length)),
                              match(colnames(cts), colnames(txi$length))]
normMat <- normMat/exp(rowMeans(log(normMat)))
o <- log(calcNormFactors(cts/normMat)) + log(colSums(cts/normMat))
y0 <- DGEList(counts=cts, group=grp)
y0$offset <- t(t(log(normMat)) + o)
y0 <- calcNormFactors(y0)
```


# Cellular component annotation of the top peaks

Using Biomart.

```{r biomart_annotation, cache = 2, warning = FALSE, eval = FALSE, include = FALSE}
### We want GO term "synapse" and then all children 
## (the different types of synapses)
## We need the GO terms for our target genes
go_tbl_sns <- biomartr::getGO(organism = "Mus musculus", 
                          genes    = unique(omni_filtered[["SNS_70K"]]$gene_id),
                          filters  = "ensembl_gene_id")

ensembl <- useMart("ensembl", dataset = "mmusculus_gene_ensembl")
## go annotation for all target genes
go_ids <- getBM(attributes = c("ensembl_gene_id", "go_id"), 
                values = unique(omni_filtered[["SNS_70K"]]$gene_id), 
                mart = ensembl)
## we only keep the genes from our initial list
go_ids <- go_ids[go_ids$ensembl_gene_id %in% unique(omni_filtered[["SNS_70K"]]$gene_id), ]
## remove all rows with go_id = ""  (no GO annotation for these IDs)
go_ids <- go_ids[go_ids$go_id != "",]


## GO database with all children per node
goccc <- as.list(GO.db::GOCCCHILDREN)
go_synapse <- "GO:0045202"
## all childern of synapse
goccc[[go_synapse]]

## GO term annotation as list
goterm <- as.list(GO.db::GOTERM)
goterm[[go_synapse]]


## get all genes with annotation "synapse"
syn_genes <- go_ids[go_ids$go_id == go_synapse,] %>% pull(ensembl_gene_id) 
length(syn_genes)
## how many genes do not have CC "synapse"?
unique(go_ids$ensembl_gene_id) %>% length() - length(syn_genes)

## annotation for all genes with CC "synapse)
go_ids_syn <- go_ids[go_ids$ensembl_gene_id %in% syn_genes,]
## we add the gene_name to the table
go_ids_syn$gene_name <- gtf$gene_name[match(go_ids_syn$ensembl_gene_id, 
                                            gtf$gene_id)]
## The genes with annotation synapse
unique(go_ids_syn$gene_name)

## add the GO term description
## some go ids do not have a GO term description!
go_ids_syn$go_term <- sapply(goterm[go_ids_syn$go_id], Term)

## save to file
# write.table(x = go_ids_syn, 
#             file = file.path(out_dir1, "SNS_70K_cutoff1e-06_GO_synapse_annotation.txt"), 
#             row.names = FALSE, sep = "\t", quote = FALSE)


## all children of "synapse"
go_ids_syn[go_ids_syn$go_id %in% goccc[[go_synapse]],] %>% dim()
## 43 annotations of "synapse" childrenm in 28 genes
go_ids_syn[go_ids_syn$go_id %in% goccc[[go_synapse]],] %>% 
  pull(go_term) %>%
  table()

go_ids_syn_child <- go_ids_syn[go_ids_syn$go_id %in% goccc[[go_synapse]],]

# write.table(x = go_ids_syn_child, 
#             file = file.path(out_dir_top, 
#                       "SNS_70K_cutoff1e-04_GO_synapse_child_annotation.txt"), 
#             row.names = FALSE, sep = "\t", quote = FALSE)

## barplot with the synaptic annotation
p <- ggplot(go_ids_syn_child, aes(x = go_term)) +
  geom_bar() +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
p
# ggsave(file.path(out_dir_top, "SNS_70K_cutoff_1e-04_GO_annotation.pdf"), 
#        p, width = 4, height = 4) 
```

# GO CC annotation with org.Mm.eg.db

```{r cc_annotation, cache = 2}
sns_target_genes <- unique(omni_filtered[["SNS_70K"]]$gene_id)

## mapping of mouse gene ids to GO terms

## convert Ensembl Gene IDs to Entrez gene ids
sns_entrez <- unlist(as.list(org.Mm.egENSEMBL2EG)[sns_target_genes])
length(sns_entrez)

## map all Entrez gene ids to GO terms
tmp <- mget(sns_entrez, org.Mm.egGO)
## filter annotation based on evidence codes
## remove all annotations that are based on elctronic annotation (IEA) 
## (not manually checked)
tmp1 <- lapply(tmp, dropECode, code = "IEA")

## select the CC annotation
tmp2 <- lapply(tmp1, getOntology, ontology = "CC")

## how many annotations per gene?
sapply(tmp2, length) %>% summary

## transform the list to a data.frame with columns:
## Entrez ID and GO term
go <- data.frame(entrez = unlist(sapply(names(tmp2), function(x) 
                                                  rep(x, length(tmp2[[x]])))),
                 GO_IDs = unlist(tmp2), stringsAsFactors = FALSE)
## add the Term
go$term <- Term(go$GO_IDs)
## add the gene name
go$gene_name <- AnnotationDbi::select(org.Mm.eg.db, keys=go$entrez, 
                                      column = "SYMBOL", 
                                      keytype = "ENTREZID")[["SYMBOL"]]

go %>%
  group_by(term) %>%
  summarise(n = n())


## for each of the annotation terms that we are intersted in, we get the list of terms of all children
## if a gene has any of the IDs, it is annotated to that node

#### Traverse the full tree to search for parent annotations
## per gene, add list of all ancestor terms to table 

go_searchs <- list(synapse = "GO:0045202", 
                  intracellular_membrane_bounded_organelle = "GO:0043231",
                  extracellular_region = "GO:0005576",
                  neuron_part = "GO:0097458",
                  GABA_ergic_synapse = "GO:0098982",
                  glutamatergic_synapse = "GO:0098978",
                  cholinergic_synapse = "GO:0098981",
                  dopaminergic_synapse = "GO:0098691",
                  endoplasmic_reticulum = "GO:0005783",
                  mitochondrion = "GO:0005739",
                  nucleus = "GO:0005634",
                  postsynapse = "GO:0098794",
                  presynapse = "GO:0098793"
                  )

goccanc <- as.list(GO.db::GOCCANCESTOR)

get_ancestors <- Vectorize(function(go_id){
  c(go_id, unlist(goccanc[[go_id]]))
})

go <- go %>% 
  as_tibble() %>%
  mutate(ancestors = get_ancestors(GO_IDs)) 
head(go)
## check for the different terms
go <- go %>%
  rowwise() %>%
  mutate(is_synapse = go_searchs[["synapse"]] %in% ancestors,
         is_intracellular_membrane_bounded_organelle = 
           go_searchs[["intracellular_membrane_bounded_organelle"]] %in% ancestors,
         is_extracellular_region = go_searchs[["extracellular_region"]] %in% ancestors,
         is_neuron_part = go_searchs[["neuron_part"]] %in% ancestors,
         is_GABA_ergic_synapse = go_searchs[["GABA_ergic_synapse"]] %in% ancestors,
         is_glutamatergic_synapse = go_searchs[["glutamatergic_synapse"]] %in% ancestors,
         is_cholinergic_synapse = go_searchs[["cholinergic_synapse"]] %in% ancestors,
         is_dopaminergic_synapse = go_searchs[["dopaminergic_synapse"]] %in% ancestors,
         is_endoplasmic_reticulum = go_searchs[["endoplasmic_reticulum"]] %in% ancestors,
         is_mitochondrion = go_searchs[["mitochondrion"]] %in% ancestors,
         is_nucleus = go_searchs[["nucleus"]] %in% ancestors,
         is_postsynapse = go_searchs[["postsynapse"]] %in% ancestors,
         is_presynapse = go_searchs[["presynapse"]] %in% ancestors
         ) 
head(go)

##
golong <- gather(go, location, is_inside, 6:18)
catCount <- golong %>% 
  group_by(entrez,location) %>% 
  summarise(is_inside = any(is_inside)) %>% 
  group_by(location) %>% 
  summarise(n=sum(is_inside))
catCount

## how many genes have annotation "synapse"?
go[go$GO_IDs %in% go_searchs["synapse"],] %>% 
  nrow()
## how many genes do not have a GO annotation:
CC_unknown <-  sum(lengths(tmp2) == 0)
CC_unknown
## how many genes could not be mapped to Entrez IDs:
unmapped_ID <- length(sns_target_genes) - length(sns_entrez)
unmapped_ID
```

## Visualization of CC categories

We visualise the results using the ggraph package from R: circlepacking and partition plot.

```{r cc_plotting, cache = 2, warning = FALSE}
from  <- c(rep("target_genes", 7), 
           rep("synapse", 4), 
           rep("intracellular_membrane_bounded_organelle", 3), 
           "neuron_part")

to <- c("unmapped_ID", "CC_unknown", "synapse", "intracellular_membrane_bounded_organelle", "extracellular_region", "neuron_part", "postsynapse",
        "GABA_ergic_synapse", "glutamatergic_synapse", "cholinergic_synapse", "dopaminergic_synapse",
        "endoplasmic_reticulum", "mitochondrion", "nucleus",
        "presynapse")
edges <- data.frame(from = from, to = to,stringsAsFactors = FALSE)

vertices <- catCount
vertices <- vertices %>% 
  dplyr::rename(name = location, size = n) %>%
  mutate(name = substring(name, 4)) %>%
  rbind(c("target_genes", length(sns_target_genes))) %>%
  rbind(c("unmapped_ID", unmapped_ID)) %>%
  rbind(c("CC_unknown", CC_unknown)) %>%
  mutate(size = as.numeric(size)) %>%
  as.data.frame()

# write.table(vertices, file.path(out_dir1, "SNS_70K_GO_CC_category_counts.txt"),
#             sep = "\t", row.names = FALSE, quote = FALSE)

## Filter the categories with 0 genes
vsn = vertices %>% dplyr::filter(size>0)
esn = edges %>% dplyr::filter(from %in% vsn$name & to %in% vsn$name)

mygraph <- graph_from_data_frame(esn, vertices= vsn)

p <- ggraph(mygraph, layout = 'circlepack', weight="size" ) + 
  geom_node_circle(aes(fill = depth)) +
  geom_node_label( aes(label=name, size=size), repel = TRUE) +
  theme_void() + 
  theme(legend.position="FALSE") + 
  scale_fill_viridis()
p
# ggsave(file.path(out_dir1, "SNS_70K_GO_CC_circlepack_origine.pdf"), p, 
#        width = 5, height = 5) 

p <- ggraph(mygraph, layout = 'circlepack', weight="size" ) + 
  geom_node_circle(aes(fill = as.factor(depth), color = as.factor(depth))) +
  geom_node_label( aes(label=name, size=size), repel = TRUE) +
  theme_void() + 
  theme(legend.position="FALSE") + 
  scale_fill_manual(values=c("0" = "white", "1" = viridis(3)[1], "2" = viridis(3)[2])) +
  scale_color_manual( values=c("0" = "white", "1" = "black", "2" = "black") ) 
p
# ggsave(file.path(out_dir1, "SNS_70K_GO_CC_circlepack.pdf"), p, 
#        width = 5, height = 5) 

## Hide the root label
# Transform it into a 'tree' format
tree <- FromDataFrameNetwork(edges)

# Then I can easily get the level of each node, and add it to the initial data frame:
mylevels=data.frame( name=tree$Get('name'), level=tree$Get("level") )
vertices = vertices %>% left_join(., mylevels, by=c("name"="name"))

# Now we can add label for level1 and 2 only for example:
vertices = vertices %>% mutate(new_label=ifelse(level==1, NA, name))

vsn = vertices %>% dplyr::filter(size>0)
esn = edges %>% dplyr::filter(from %in% vsn$name & to %in% vsn$name)
mygraph <- graph_from_data_frame( esn, vertices=vsn)


p <- ggraph(mygraph, layout = 'circlepack', weight="size" ) + 
  geom_node_circle(aes(fill = depth)) +
  geom_node_label( aes(label=new_label, size=size), repel = TRUE) +
  theme_void() + 
  theme(legend.position="FALSE") + 
  scale_fill_viridis()
p
# ggsave(file.path(out_dir1, "SNS_70K_GO_CC_circlepack_label.pdf"), p, 
#        width = 5, height = 5) q
  

### partition
## TODO
## add 2nd level to neuron_part otherwise the sizes are not correct 
## (at least 2 categories per level)

p <- ggraph(mygraph, 'partition', weight = "size", circular = TRUE) + 
  geom_node_arc_bar(aes(fill = depth)) +
  geom_node_label( aes(label=new_label), repel = TRUE) +
  theme_void() +
  theme(legend.position="none")
p
# ggsave(file.path(out_dir1, "SNS_70K_GO_CC_partition.pdf"), p, 
#        width = 5, height = 5) 

p <- ggraph(mygraph, layout = 'treemap', weight = "size") + 
  geom_node_tile(aes(fill = depth)) +
  geom_node_label( aes(label=name, size=size)) +
  theme_void() + 
  theme(legend.position="FALSE") + 
  scale_fill_viridis()
p
# ggsave(file.path(out_dir1, "SNS_70K_GO_CC_treemap.pdf"), p, 
#        width = 5, height = 5) 
```

# GO annotation over-representation analysis
## SNS targets

Which GO CC annotations are over-represented among our target genes? We use the `goana()` function from the `limma` package. The returned p-values are unadjusted for multiple testing, because GO terms and KEGG pathways are often overlapping, so standard methods may be very conservative. The authors suggest taht only very small p-values should be used for publications. Gordon Smyth said the following [online](https://support.bioconductor.org/p/74899/): "Yes, the p-values need adjustment in principle, but I prefer to do this informally -- I only take notice of p-values that are less than 1e-8 and preferably smaller."

`goana` computes one-sided hypergeometric tests. The returned values are the following:

* `Term`: the GO term
* `N`: the number if genes in the GO term
* `DE`: number of genes in the target set
* `P.DE`: p-value for over-representation of the GO term in the set.

```{r go_enrichment_sns, cache = 2, eval = TRUE}
sns_target_genes <- unique(omni_filtered[["SNS_70K"]]$gene_id)

## convert the Ensembl Gene IDs to entrez Gene IDs with Biomart
ensembl <- useMart("ensembl")
ensembl <- useDataset("mmusculus_gene_ensembl", mart = ensembl)
entrez_sns <- getBM(attributes = c("ensembl_gene_id","entrezgene"), 
             values = sns_target_genes, mart = ensembl )
## we only keep the genes from our initial list
entrez_sns <- entrez_sns[entrez_sns$ensembl_gene_id %in% sns_target_genes, ]

## Not all mRNAs are present in the SNS sample, so we take all expressed genes 
## >=1cpm in RNA-seq as background.
y0_sns <- y0
keep <- rowSums(cpm(y0_sns)>1) == 2 
y_sns <- y0_sns[keep, , keep.lib.sizes = FALSE]
dim(y_sns)
sns_bg <- rownames(y_sns)

## convert to Entrez IDs
sns_bg_entrez <- getBM(attributes = c("ensembl_gene_id","entrezgene"), 
             values = sns_bg, mart = ensembl )
sns_bg_entrez <- sns_bg_entrez[sns_bg_entrez$ensembl_gene_id %in% sns_bg, ]

## GO analysis with goana 
goana_sns <- goana(de = unique(entrez_sns$entrezgene), species = "Mm",
                   universe = sns_bg_entrez$entrezgene)
goana_sns <- goana_sns[order(goana_sns$P.DE, decreasing = FALSE),]
## What are the most enriched annotation terms?
topGO(goana_sns, ontology = "CC", number = 10)

# What are the genes that have annotation "synapse"?
# x <- org.Mm.egGO2ALLEGS
# Rkeys(x) <- "GO:0045202"
# EG <- mappedLkeys(x)
# intersect(EG, entrez_sns$entrezgene)

## Match gene length to bg list
genes <- gtf[gtf$type == "gene"]
m <- match(sns_bg_entrez$ensembl_gene_id, genes$gene_id)
gene_length <- width(genes)[m]
## using gene length as covariate
goana_sns <- goana(de = unique(entrez_sns$entrezgene), species = "Mm", 
                   universe = sns_bg_entrez$entrezgene, covariate = gene_length)
goana_sns <- goana_sns[order(goana_sns$P.DE, decreasing = FALSE),]
## What are the most enriched annotation terms?
topGO(goana_sns, ontology = "CC", number = 20)
topGO(goana_sns, ontology = "BP", number = 10)
topGO(goana_sns, ontology = "MF", number = 10)

write.table(topGO(goana_sns, ontology = "CC", number = 100), 
            file.path(out_dir_top, "GO_ORA", "SNS_70K_goana_CC.txt"),
            sep = "\t", quote = FALSE)
write.table(topGO(goana_sns, ontology = "BP", number = 100), 
            file.path(out_dir_top, "GO_ORA", "SNS_70K_goana_BP.txt"),
            sep = "\t", quote = FALSE)
write.table(topGO(goana_sns, ontology = "MF", number = 100), 
            file.path(out_dir_top, "GO_ORA", "SNS_70K_goana_MF.txt"),
            sep = "\t", quote = FALSE)
```


## Enriched KEGG pachways

```{r kegg_pathway_enrichment, cache = 2, eval = TRUE}
## one-sided hypergeometric tests

## SNS
kegga_sns<- kegga(de = unique(entrez_sns$entrezgene), species = "Mm",
                   universe = sns_bg_entrez$entrezgene)
## sort the pathways after raw p-value
kegga_sns <- kegga_sns[order(kegga_sns$P.DE, decreasing = FALSE),]
topKEGG(kegga_sns, number = 20)
write.table(topKEGG(kegga_sns, number = 100), 
            file.path(out_dir_top, "GO_ORA", "SNS_70K_kegga.txt"),
            sep = "\t", quote = FALSE)


# ## Homogenate
# kegga_homo <- kegga(de = unique(entrez_homo$entrezgene), species = "Mm",
#                    universe = homo_bg_entrez$entrezgene)
# ## sort the pathways after raw p-value
# kegga_homo <- kegga_homo[order(kegga_homo$P.DE, decreasing = FALSE),]
# topKEGG(kegga_homo, number = 20)
# write.table(topKEGG(kegga_homo, number = 100), 
#             file.path(out_dir_top, "GO_ORA", "HOMO_70K_kegga.txt"),
#             sep = "\t", quote = FALSE)
```


## KEGG pathway visualization

```{r kegg_pathways, cache = 2, eval = TRUE}
## We pick the following pathways:
# 04724 glutamergic
# 04725 cholinergic
# 04726 serotonergic
# 04727 GABAergic
# 04728 dopaminergic
## KEGG pathway numbers
pwlist <- paste0("0",seq(4724,4728))
sns_target_genes <- unique(omni_filtered[["SNS_70K"]]$gene_id)

# kegg_ids <- getBM(attributes = c("ensembl_gene_id", "kegg_enzyme"), 
#                 values = sns_target_genes, 
#                 mart = ensembl)
# kegg_ids <- kegg_ids[kegg_ids$ensembl_gene_id %in% sns_target_genes, ]
# ## remove all rows with go_id = ""
# kegg_ids <- kegg_ids[kegg_ids$kegg_enzyme != "",]

### Pathview visualization of KEGG pathways
data(gene.idtype.list)
# gene.idtype.list  ## Ensembl IDs are supported

## All genes in the list have the same number (1) associated with them
pvdata <- rep(1,length(sns_target_genes))
names(pvdata) <- sns_target_genes
pv.out <- pathview(gene.data = pvdata, pathway.id = pwlist, species = 'mmu', 
                   gene.idtype = "ENSEMBL")
```


## goSTAG over-representation analysis

Visualization of the ORA analysis by clustering the GO terms.

```{r goSTAG, cache = 2, eval = FALSE}
## Prepare the target lists
## We need the gene_name and not the Ensembl ID
gene_lists <- list(SNS = unique(gtf$gene_name[gtf$gene_id %in% 
                                                sns_target_genes]))

## Prepare the GO terms we use the archived annotation, because it takes a very
## long time to get the current annotations from Biomart
go_terms <- loadGOTerms(use_archived = TRUE, species = "mouse", 
                        domain = "CC", min_num_genes = 5)

## Running goSTAG
## All GO terms where none of the samples have a p-value < 0.05 are removed
enrichment_matrix <- performGOEnrichment(gene_lists, go_terms)
head(enrichment_matrix)
dim(enrichment_matrix)
## Filtering by FDR
enrichment_matrix_FDR <- performGOEnrichment(gene_lists, go_terms, 
                                             filter_method = "p.adjust", 
                                             significance_threshold = 0.1, 
                                             p.adjust_method = "BH" )
dim(enrichment_matrix_FDR)

## hierarchical clustering of GO terms
hclust_results <- performHierarchicalClustering(enrichment_matrix_FDR)
hclust_results

## Euclidean distance and complete agglomeration
hclust_results_euclidean <- 
  performHierarchicalClustering(enrichment_matrix_FDR, 
                                distance_method = "euclidean", 
                                clustering_method = "complete" )

## grouping the clusters
## decreasing the distance_threshold leads to more clusters
clusters <- groupClusters(hclust_results_euclidean, distance_threshold = 0.7)
lapply(head(clusters), head)
length(clusters)

## Annotating the clusters
## annotate each of the clusters using the GO term within each cluster’s subtree
## that has the most paths back to the root
cluster_labels <- annotateClusters( clusters )
head(cluster_labels)
```

```{r goSTAG_plotting, cache = 2, eval = FALSE}
## Plotting
## Only label GO clusters with more than 2 GO terms
plotHeatmap(enrichment_matrix_FDR, hclust_results_euclidean, clusters, 
            cluster_labels, min_num_terms = 2)

plotHeatmap(enrichment_matrix_FDR, hclust_results_euclidean, clusters, 
            cluster_labels, min_num_terms = 1)
```